\addcontentsline{toc}{chapter}{Certification of Approval}
% Page 3 : Approval of the DSC
\thispagestyle{empty}
\begin{center}
	\textbf{\Large APPROVAL OF THE VIVA-VOCE BOARD}
\end{center}
\begin{flushright}
	DD/MM/YYYY
\end{flushright}
~~~Certified that the thesis entitled  \textbf{Incremental Security Enforcement for Underwater Drones}, submitted by \textbf{Vedanta Mohapatra} to the Indian Institute of Technology  Bhubaneswar, for the award of the degree of Doctor of Philosophy has been accepted by the external examiners and that the student has successfully defended the thesis in the viva-voce examination held today.
\begin{center}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}cccccccc}
		&&&&&&&\\
		&&&&&&&\\
		\multicolumn{2}{c}{(Member of DSC)} && \multicolumn{2}{c}{(Member of DSC)} && \multicolumn{2}{c}{(Member of DSC)}\\
		&&&&&&&\\
		&&&&&&&\\
		\multicolumn{3}{c}{} &&& \multicolumn{3}{c}{(Supervisor)}\\
		% Comment the above line and uncomment the lower one if you have two supervisors
		% \multicolumn{3}{c}{(Supervisor)} &&& \multicolumn{3}{c}{(Supervisor)}\\
		&&&&&&&\\
		&&&&&&&\\
		\multicolumn{3}{c}{(External Examiner)} &&& \multicolumn{3}{c}{(Chairman)}\\
	\end{tabular*}
\end{center}

%% Page 4 : Blank
\newpage
%\thispagestyle{empty}
%\cleardoublepage

\addcontentsline{toc}{chapter}{Certificate}
% Page 5: Certificate on department letterhead
\thispagestyle{empty}
{~} % Buffer blank character to prevent horizontal underflow due to next \vspace
\vspace{10em} % Increase if the dept. letterhead requires more space
\begin{center}
	\textbf{\Large CERTIFICATE}
\end{center}
~~~This is to certify that the thesis entitled  \textbf{Write Thesis Title Here}, submitted by \textbf{Student Name} to Indian Institute of Technology  Bhubaneswar, is a record of bonafide research work under my supervision and I consider it worthy of consideration for the award of the degree of Doctor of Philosophy of the Institute.

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}ll}
	&\\
	&\\
	&\\
	Date : & \textbf{Supervisor Name}\\
	& Designation\\
	& School of ******* Sciences \\
	& Indian Institute of Technology Bhubaneswar \\
	& Bhubaneswar, India \\
	% Comment the above line and uncomment the lower one if you have two supervisors
	% (Supervisor) & (Supervisor)\\
\end{tabular*}



%% Page 6 : Blank
\newpage
%\thispagestyle{empty}
%\cleardoublepage

\addcontentsline{toc}{chapter}{Declaration}
% Page 7: Declaration
\thispagestyle{empty}
\begin{center}
	\textbf{\Large DECLARATION}
\end{center}
I certify that
\begin{enumerate}[a.]
	\item the work contained in the thesis is original and has been done by myself under the general supervision of my supervisor.
	\item the work has not been submitted to any other institute for any degree or diploma.
	\item I have followed the guidelines provided by the institute in writing the thesis.
	\item I have conformed to the norms and guidelines given in the ethical code of conduct of the institute.
	\item whenever I have used materials (data, theoretical analysis, and text) from other sources, I have given due credit to them by citing them in the text of the thesis and giving their details in the references.
	\item whenever I have quoted written materials from other sources, I have put them under quotation marks and given due credit to the sources by citing them and giving required details in the references.
\end{enumerate}
\vspace{4em}
\begin{flushright}
	Student Name
\end{flushright}

%% Page 8 : Blank
\newpage


\addcontentsline{toc}{chapter}{Acknowledgments}
% Page 11 : Acknowledgment
\thispagestyle{empty}
\begin{center}
	\textbf{\Large Acknowledgments}
\end{center}

Write Acknowledgments Here


\vspace{3em}
\begin{flushright}
	Student Name
\end{flushright}
